---
title: "A systematic review and meta-analysis of dopaminergic agonists for anhedonia - results from human studies"
output: html_document
date: "2024-03-11"
author: "First draft by Jaycee Kennett, Claire Friedrich, Ava Homiar, Charlotte Austin <span style='font-size: 15px'></style>"
mainfont: Arialh
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of the methodological approach

For this review, The team searched for all controlled and uncontrolled studies that examined dopaminergic agonists. In the first iteration of the review consisted of analyzing any usable data from randomized controlled studies that compared any dopaminergic agonists to placebo in individuals with a diagnosis of depressive disorder or major depressive disorder. Specifically, the team aimed to assess the recorded measures of anhedonia that were measured using scales such as the MADRS Anhedonia Factor, MEI Total and IDS Pleasure scales. We examines efficacy outcomes, including symptoms of anhedonia and anxiety (primary outcomes) and symptom domains, dropouts due to any reason, and adverse events.

## Description of included studies

There were 61 eligible studies that were extracted and appraised. The study characteristics can be found in **Table 1**. Data from 6 studies were analyzed (total of #participants), which included adults that participates from multiple countries. All studies were sponsored by pharmaceutical companies that were manufacturing the dopaminergic agonists. The studies included 2 to 3 arms of administering the dopaminergic agonist (i.e. Amitifadine, Bupropion, or Bupropion XR) with a constant or increasing dose, which also included a comparison to placebo. These pharmacological interventions were delivered to individuals with depressive disorder or major depressive disorder and healthy volunteers. All studies consisted of a treatment duration lasting between 6 to 10 weeks, with placebo. One study administered the agonist for 6 weeks, 3 studies administered the agonist for 8 weeks, and 2 administered the agonist for 10 weeks. Of the 6 studies, 3 administered a fixed dosage, while the other 2 administered a flexible dosage. All studies had an oral intervention format, with a delivered dosage range of 25mg-50mg for Amitifadine, and 150mg-300mg for Bupropion and Bupropion XR. 

## Risk of Bias assessment

The risk of bias of the studies was examined using the ROB2 tool for all outcomes in the studies.

```{r echo=FALSE, include=FALSE}
#set working directory
setwd("C:/Users/jkennett/Documents/GitHub/LSR1_anhedonia_H")

#open rds data file
df <- readRDS("~/GitHub/LSR1_anhedonia_H/rds/human/df.rds")

#load packages
library(meta)

# functions ----
## remove one-arm studies
remove.onearm <- function(data, warn = T) {
  # Remove 1-arm studies
  sel <- as.logical(sapply(data[,'studlab'],
                           function(study) {sum(data[,'studlab'] == study, na.rm = T) > 1
                           }))
  
  if (warn && !all(sel)) {
    warning(paste('Removed', sum(!sel), 'one-arm studies:',
                  paste(data[!sel,'studlab'], collapse=', ')))
  }
  data[sel, , drop = F]
}
## collapse arms - binary
collapse.arms.binary <- function(data) {
  data3.2 = data[, c(which(colnames(data)=='studlab'), 
                     which(colnames(data)=='treatment'),
                     which(colnames(data)=='arm'))]
  data3.31 = data[, c(which(colnames(data)=='n'),
                      which(colnames(data)=='r'))]
  data3.32 = data[, c(which(colnames(data)=='age_mean'),
                      which(colnames(data)=='female_prop'),
                      which(colnames(data)=='anhedonia_baseline_mean'), 
                      which(colnames(data)=='anxiety_baseline_mean'), 
                      which(colnames(data)=='reward_baseline_mean'), 
                      which(colnames(data)=='tx_duration'))]
  data3.41 = aggregate(x = data3.31, by = list(data3.2$studlab, data3.2$treatment, data3.2$arm), FUN = sum)
  data3.42 = aggregate(x = data3.32, by = list(data3.2$studlab, data3.2$treatment), FUN = mean)
  data3.4 = merge(x = data3.41, y = data3.42, by = c('Group.1', 'Group.2'))
  colnames(data3.4) = c('studlab', 
                        'treatment', 
                        'arm', 
                        'n', 
                        'r', 
                        'age_mean', 
                        'female_prop', 
                        'anhedonia_baseline_mean', 
                        'anxiety_baseline_mean', 
                        'reward_baseline_mean', 
                        'tx_duration')
  data3.4 <- data3.4[with(data3.4, order(studlab, arm)), ]
  return(data3.4)
  #return.list = list('data_collapsed' = data3.4)
  #return(return.list)
}

## collapse arms - continuous
collapse.arms.continuous <- function(data) {
  data3.2 = data[, c(which(colnames(data)=='studlab'), 
                     which(colnames(data)=='treatment'),
                     which(colnames(data)=='arm'))]
  data3.31 = data[, which(colnames(data)=='n')]
  data3.32 = data[, c(which(colnames(data)=='mean'), 
                      which(colnames(data)=='sd'), 
                      which(colnames(data)=='age_mean'),
                      which(colnames(data)=='female_prop'),
                      which(colnames(data)=='anhedonia_baseline_mean'), 
                      which(colnames(data)=='anxiety_baseline_mean'), 
                      which(colnames(data)=='reward_baseline_mean'), 
                      which(colnames(data)=='tx_duration'))]
  data3.41 = aggregate(x = data3.31, by = list(data3.2$studlab, data3.2$treatment, data3.2$arm), FUN = sum)
  data3.42 = aggregate(x = data3.32, by = list(data3.2$studlab, data3.2$treatment), FUN = mean)
  data3.4 = merge(x = data3.41, y = data3.42, by = c('Group.1', 'Group.2'))
  colnames(data3.4) = c('studlab', 
                        'treatment', 
                        'arm', 
                        'n', 
                        'mean', 
                        'sd', 
                        'age_mean', 
                        'female_prop', 
                        'anhedonia_baseline_mean', 
                        'anxiety_baseline_mean', 
                        'reward_baseline_mean', 
                        'tx_duration')
  data3.4 <- data3.4[with(data3.4, order(studlab, arm)), ]
  return(data3.4)
  #return.list = list('data_collapsed' = data3.4)
  #return(return.list)
}

## collapse arms - continuous
collapse.arms.continuous.short <- function(data) {
  data3.2 = data[, c(which(colnames(data)=='studlab'), 
                     which(colnames(data)=='treatment'),
                     which(colnames(data)=='arm'))]
  data3.31 = data[, which(colnames(data)=='n')]
  data3.32 = data[, c(which(colnames(data)=='mean'), 
                      which(colnames(data)=='sd'))]
  data3.41 = aggregate(x = data3.31, by = list(data3.2$studlab, data3.2$treatment, data3.2$arm), FUN = sum)
  data3.42 = aggregate(x = data3.32, by = list(data3.2$studlab, data3.2$treatment), FUN = mean)
  data3.4 = merge(x = data3.41, y = data3.42, by = c('Group.1', 'Group.2'))
  colnames(data3.4) = c('studlab', 
                        'treatment',
                        'arm', 
                        'n', 
                        'mean', 
                        'sd')
  data3.4 <- data3.4[with(data3.4, order(studlab, arm)), ]
  return(data3.4)
  #return.list = list('data_collapsed' = data3.4)
  #return(return.list)
}

# drugs ----
IMAO = c('isocarboxazid', 'phenelzine', 'tranylcypromine', 'selegiline')
RIMA = c('brofaromine', 'minaprine', 'moclobemide')
DRI = c('bupropion', 'dextromethorphan-bupropion', 'amitifadine', 'gsk372475', 'methylphenidate')
agonist = c('memantine', 'ropinirole', 'pramipexole')
vescicular = ('rx-10100')

df <- readRDS('rds/human/df.rds')

```

### Primary outcome: reduction in anhedonia scores at 4-12 weeks

```{r echo=FALSE, include=FALSE}

#run anheo
# anhedonia ----
df.anhedonia <- df[!is.na(df$anhedonia_followup_mean), c('studlab', 
                                                         'treatment', 
                                                         'treatment_details', 
                                                         'anhedonia_followup_n', 
                                                         'anhedonia_followup_mean', 
                                                         'anhedonia_followup_sd', 
                                                         'anhedonia_followup_type', 
                                                         'anhedonia_followup_scale', 
                                                         'anhedonia_followup_direction', 
                                                         'age_mean',
                                                         'female_prop',
                                                         'anhedonia_baseline_mean',
                                                         'anxiety_baseline_mean',
                                                         'reward_baseline_mean',
                                                         'tx_duration',
                                                         'arm')]
df.anhedonia$anhedonia_followup_mean[df.anhedonia$anhedonia_followup_direction=='positive'] <- df.anhedonia$anhedonia_followup_mean[df.anhedonia$anhedonia_followup_direction=='positive']*-1
colnames(df.anhedonia) <- c('studlab', 
                            'treatment', 
                            'treatment_details', 
                            'n', 
                            'mean', 
                            'sd', 
                            'anhedonia_followup_type', 
                            'anhedonia_followup_scale', 
                            'anhedonia_followup_direction', 
                            'age_mean',
                            'female_prop',
                            'anhedonia_baseline_mean',
                            'anxiety_baseline_mean',
                            'reward_baseline_mean',
                            'tx_duration',
                            'arm')
df.anhedonia <- remove.onearm(df.anhedonia)
df.anhedonia.merged <- collapse.arms.continuous(df.anhedonia)
df.pw.anhedonia <- netmeta::pairwise(studlab = studlab,
                                     treat = treatment,
                                     n = n,
                                     mean = mean,
                                     sd = sd,
                                     data = df.anhedonia.merged,
                                     sm = 'SMD')
df.pw.anhedonia$age <- rowMeans(df.pw.anhedonia[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.anhedonia$female_prop <- rowMeans(df.pw.anhedonia[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.anhedonia$anhedonia_baseline <- rowMeans(df.pw.anhedonia[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.anhedonia$anxiety_baseline <- rowMeans(df.pw.anhedonia[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.anhedonia$reward_baseline <- rowMeans(df.pw.anhedonia[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.anhedonia$colour <- ifelse(df.pw.anhedonia$treat1 %in% IMAO, 
                               'red', 
                               ifelse(df.pw.anhedonia$treat1 %in% RIMA,
                                      'orange',
                                      ifelse(df.pw.anhedonia$treat1 %in% DRI,
                                             'deepskyblue',
                                             ifelse(df.pw.anhedonia$treat1 %in% agonist,
                                                    'purple',
                                                    ifelse(df.pw.anhedonia$treat1 %in% vescicular,
                                                    'green4',
                                                    'grey'
                                      )))))
#run anhedonia meta-analysis
pwma.anhedonia <- metacont(n.e = n1, 
                           mean.e = mean1, 
                           sd.e = sd1, 
                           n.c = n2, 
                           mean.c = mean2, 
                           sd.c = sd2, 
                           studlab = studlab, 
                           data = df.pw.anhedonia, 
                           sm = 'SMD', 
                           method.smd = 'Hedges', 
                           comb.fixed = F, 
                           comb.random = T, 
                           title = 'Anhedonia',
                           prediction = T, 
                           hakn = T, 
                           method.tau = 'REML')


```

```{r echo=FALSE, fig.width=12, fig.height=4}
forest(pwma.anhedonia, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'Anhedonia symptoms severity',
       col.square = pwma.anhedonia$data$colour
       #lower.equi = -0.20, upper.equi = 0.20, 
       #col.equi = '#F8F8F8', 
       #fill.lower.equi = c("#E4EBF4", "#F8F8F8"),
       #fill.upper.equi = c("#F8F8F8", "#EFE6ED")
       )
```

**Figure X** Forest plot for symptoms of anhedonia (primary outcome) comparing dopaminergic agonists vs placebo for individuals with anhedonia at 4-12 weeks (primary timepoint). SMD: standardised mean difference, 95%CI: 95% confidence intervals, SD: standard deviation.

### Secondary outcome: Reduction in mean anxiety score at 4-12 weeks

```{r echo=FALSE, include=FALSE}
# anxiety ----
df.anxiety <- df[!is.na(df$anxiety_followup_mean), c('studlab', 
                                                     'treatment', 
                                                     'treatment_details', 
                                                     'anxiety_followup_n', 
                                                     'anxiety_followup_mean', 
                                                     'anxiety_followup_sd', 
                                                     'anxiety_followup_type', 
                                                     'anxiety_followup_scale', 
                                                     'anxiety_followup_direction', 
                                                     'age_mean',
                                                     'female_prop',
                                                     'anhedonia_baseline_mean',
                                                     'anxiety_baseline_mean',
                                                     'reward_baseline_mean',
                                                     'tx_duration',
                                                     'arm')]
df.anxiety$anxiety_followup_mean[df.anxiety$anxiety_followup_direction=='positive'] <- df.anxiety$anxiety_followup_mean[df.anxiety$anxiety_followup_direction=='positive']*-1
colnames(df.anxiety) <- c('studlab', 
                          'treatment', 
                          'treatment_details', 
                          'n', 
                          'mean', 
                          'sd', 
                          'anxiety_followup_type', 
                          'anxiety_followup_scale', 
                          'anxiety_followup_direction',
                          'age_mean',
                          'female_prop',
                          'anhedonia_baseline_mean',
                          'anxiety_baseline_mean',
                          'reward_baseline_mean',
                          'tx_duration',
                          'arm')
df.anxiety <- remove.onearm(df.anxiety)
df.anxiety.merged <- collapse.arms.continuous(df.anxiety)
df.pw.anxiety <- netmeta::pairwise(studlab = studlab,
                                   treat = treatment,
                                   n = n,
                                   mean = mean,
                                   sd = sd,
                                   data = df.anxiety.merged,
                                   sm = 'SMD')
df.pw.anxiety$age <- rowMeans(df.pw.anxiety[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.anxiety$female_prop <- rowMeans(df.pw.anxiety[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.anxiety$anhedonia_baseline <- rowMeans(df.pw.anxiety[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.anxiety$anxiety_baseline <- rowMeans(df.pw.anxiety[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.anxiety$reward_baseline <- rowMeans(df.pw.anxiety[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.anxiety$colour <- ifelse(df.pw.anxiety$treat1 %in% IMAO, 
                               'red', 
                               ifelse(df.pw.anxiety$treat1 %in% RIMA,
                                      'orange',
                                      ifelse(df.pw.anxiety$treat1 %in% DRI,
                                             'deepskyblue',
                                             ifelse(df.pw.anxiety$treat1 %in% agonist,
                                                    'purple',
                                                    ifelse(df.pw.anxiety$treat1 %in% vescicular,
                                                    'green4',
                                                    'grey'
                                             )))))
df.pw.anxiety$group <- ifelse(df.pw.anxiety$colour=='red',
                          'MAOI',
                          ifelse(df.pw.anxiety$colour=='orange',
                                 'RIMA',
                                 ifelse(df.pw.anxiety$colour=='deepskyblue',
                                        '*DRI',
                                        ifelse(df.pw.anxiety$colour=='purple',
                                               'Agonist',
                                               ifelse(df.pw.anxiety$colour=='green4',
                                                      'Vesicle transport facilitator',
                                                      'Other')))))
#run anxiety meta-analysis
pwma.anxiety <- metacont(n.e = n1, 
                         mean.e = mean1, 
                         sd.e = sd1, 
                         n.c = n2, 
                         mean.c = mean2, 
                         sd.c = sd2, 
                         studlab = studlab, 
                         data = df.pw.anxiety, 
                         sm = 'SMD', 
                         method.smd = 'Hedges', 
                         comb.fixed = F, 
                         comb.random = T, 
                         title = 'Anxiety',
                         prediction = T, 
                         hakn = T, 
                         method.tau = 'REML',
                         subgroup = group)
```
```{r echo=FALSE, fig.width=12, fig.height=8}
forest(pwma.anxiety, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'Anxiety symptoms severity',
       col.square = pwma.anxiety$data$colour
       #lower.equi = -0.20, upper.equi = 0.20, 
       #col.equi = '#F8F8F8', 
       #fill.lower.equi = c("#E4EBF4", "#F8F8F8"),
       #fill.upper.equi = c("#F8F8F8", "#EFE6ED")
)
```

**Figure X** Forest plot for symptoms of anxiety (secondary outcome) comparing dopaminergic agonists vs placebo for individuals with anxiety at 4-12 weeks (primary timepoint). SMD: standardised mean difference, 95%CI: 95% confidence intervals, SD: standard deviation.

### Secondary outcome: Dropouts due to any reason

```{r echo=FALSE, include=FALSE}
# acceptability ----
df.acc <- df[!is.na(df$r_acceptability), c('studlab', 
                                           'treatment', 
                                           'treatment_details', 
                                           'n_randomised', 
                                           'r_acceptability',
                                           'age_mean',
                                           'female_prop',
                                           'anhedonia_baseline_mean',
                                           'anxiety_baseline_mean',
                                           'reward_baseline_mean',
                                           'tx_duration',
                                           'arm')]
colnames(df.acc) <- c('studlab', 
                      'treatment', 
                      'treatment_details', 
                      'n', 
                      'r',
                      'age_mean',
                      'female_prop',
                      'anhedonia_baseline_mean',
                      'anxiety_baseline_mean',
                      'reward_baseline_mean',
                      'tx_duration',
                      'arm')
df.acc$treatment_details <- tolower(df.acc$treatment_details)
df.acc$treatment_details <- ifelse(df.acc$treatment_details=='placebo', 'placebo', 'active')
df.acc <- df.acc[-(is.na(df.acc$n)), ]
df.acc <- remove.onearm(df.acc)
df.acc.merged <- collapse.arms.binary(df.acc)
df.pw.acc <- netmeta::pairwise(studlab = studlab,
                               treat = treatment,
                               n = n,
                               event = r,
                               data = df.acc.merged,
                               sm = 'OR')
df.pw.acc$age <- rowMeans(df.pw.acc[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.acc$female_prop <- rowMeans(df.pw.acc[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.acc$anhedonia_baseline <- rowMeans(df.pw.acc[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.acc$anxiety_baseline <- rowMeans(df.pw.acc[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.acc$reward_baseline <- rowMeans(df.pw.acc[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.acc$colour <- ifelse(df.pw.acc$treat1 %in% IMAO, 
                           'red', 
                           ifelse(df.pw.acc$treat1 %in% RIMA,
                                  'orange',
                                  ifelse(df.pw.acc$treat1 %in% DRI,
                                         'deepskyblue',
                                         ifelse(df.pw.acc$treat1 %in% agonist,
                                                'purple',
                                                ifelse(df.pw.acc$treat1 %in% vescicular,
                                                'green4',
                                                'grey'
                                         )))))
df.pw.acc$group <- ifelse(df.pw.acc$colour=='red',
                          'MAOI',
                          ifelse(df.pw.acc$colour=='orange',
                                 'RIMA',
                                 ifelse(df.pw.acc$colour=='deepskyblue',
                                        '*DRI',
                                        ifelse(df.pw.acc$colour=='purple',
                                               'Agonist',
                                               ifelse(df.pw.acc$colour=='green4',
                                                      'Vesicle transport facilitator',
                                                      'Other')))))
#run acceptability meta-analysis
pwma.acc <- metabin(n.e = n1, 
                    event.e = event1, 
                    n.c = n2, 
                    event.c = event2, 
                    studlab = studlab, 
                    data = df.pw.acc, 
                    sm = 'OR', 
                    comb.fixed = F, 
                    comb.random = T, 
                    title = 'Acceptability',
                    prediction = T, 
                    hakn = T, 
                    method.tau = 'REML',
                    subgroup = group)
```


```{r echo=FALSE, fig.width=12, fig.height=14}
forest(pwma.acc, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'Dropout due to any reasons',
       col.square = pwma.acc$data$colour
)
```

**Figure X** Forest plot for dropouts due to any reason for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

### Secondary outcome: dropouts due to side effects

```{r echo=FALSE, include=FALSE}
# tolerability ----
df.tol <- df[!is.na(df$r_tolerability), c('studlab', 
                                          'treatment', 
                                          'treatment_details', 
                                          'n_randomised', 
                                          'r_tolerability',
                                          'age_mean',
                                          'female_prop',
                                          'anhedonia_baseline_mean',
                                          'anxiety_baseline_mean',
                                          'reward_baseline_mean',
                                          'tx_duration',
                                          'arm')]
colnames(df.tol) <- c('studlab', 
                      'treatment', 
                      'treatment_details', 
                      'n', 
                      'r',
                      'age_mean',
                      'female_prop',
                      'anhedonia_baseline_mean',
                      'anxiety_baseline_mean',
                      'reward_baseline_mean',
                      'tx_duration',
                      'arm')
df.tol$treatment_details <- tolower(df.tol$treatment_details)
df.tol$treatment_details <- ifelse(df.tol$treatment_details=='placebo', 'placebo', 'active')
df.tol <- remove.onearm(df.tol)
df.tol.merged <- collapse.arms.binary(df.tol)
df.pw.tol <- netmeta::pairwise(studlab = studlab,
                               treat = treatment,
                               n = n,
                               event = r,
                               data = df.tol.merged,
                               sm = 'OR')
df.pw.tol$age <- rowMeans(df.pw.tol[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.tol$female_prop <- rowMeans(df.pw.tol[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.tol$anhedonia_baseline <- rowMeans(df.pw.tol[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.tol$anxiety_baseline <- rowMeans(df.pw.tol[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.tol$reward_baseline <- rowMeans(df.pw.tol[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.tol$colour <- ifelse(df.pw.tol$treat1 %in% IMAO, 
                           'red', 
                           ifelse(df.pw.tol$treat1 %in% RIMA,
                                  'orange',
                                  ifelse(df.pw.tol$treat1 %in% DRI,
                                         'deepskyblue',
                                         ifelse(df.pw.tol$treat1 %in% agonist,
                                                'purple',
                                                ifelse(df.pw.tol$treat1 %in% vescicular,
                                                'green4',
                                                'grey'
                                         )))))
df.pw.tol$group <- ifelse(df.pw.tol$colour=='red',
                          'MAOI',
                          ifelse(df.pw.tol$colour=='orange',
                                 'RIMA',
                                 ifelse(df.pw.tol$colour=='deepskyblue',
                                        '*DRI',
                                        ifelse(df.pw.tol$colour=='purple',
                                               'Agonist',
                                               ifelse(df.pw.tol$colour=='green4',
                                                      'Vesicle transport facilitator',
                                                      'Other')))))
#run tolerability meta-analysis
pwma.tol <- metabin(n.e = n1, 
                    event.e = event1, 
                    n.c = n2, 
                    event.c = event2, 
                    studlab = studlab, 
                    data = df.pw.tol, 
                    sm = 'OR', 
                    comb.fixed = F, 
                    comb.random = T, 
                    title = 'tolerability',
                    prediction = T, 
                    hakn = T, 
                    method.tau = 'REML',
                    subgroup = group)
```

```{r echo=FALSE, fig.width=12, fig.height=14}

forest(pwma.tol, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'Dropout due to side effects',
       col.square = pwma.tol$data$colour
)
```

**Figure X** Forest plot for dropouts due to side effects for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

### Secondary outcome: nausea
```{r echo=FALSE, include=FALSE}
#nausea
df.nausea <- df[!is.na(df$nausea), c('studlab', 
                                     'treatment', 
                                     'treatment_details', 
                                     'n_randomised', 
                                     'nausea',
                                     'age_mean',
                                     'female_prop',
                                     'anhedonia_baseline_mean',
                                     'anxiety_baseline_mean',
                                     'reward_baseline_mean',
                                     'tx_duration',
                                     'arm')]
colnames(df.nausea) <- c('studlab', 
                      'treatment', 
                      'treatment_details', 
                      'n', 
                      'r',
                      'age_mean',
                      'female_prop',
                      'anhedonia_baseline_mean',
                      'anxiety_baseline_mean',
                      'reward_baseline_mean',
                      'tx_duration',
                      'arm')
df.nausea$treatment_details <- tolower(df.nausea$treatment_details)
df.nausea$treatment_details <- ifelse(df.nausea$treatment_details=='placebo', 'placebo', 'active')
df.nausea <- remove.onearm(df.nausea)
df.nausea.merged <- collapse.arms.binary(df.nausea)
df.pw.nausea <- netmeta::pairwise(studlab = studlab,
                                  treat = treatment,
                                  n = n,
                                  event = r,
                                  data = df.nausea.merged,
                                  sm = 'OR')
df.pw.nausea$age <- rowMeans(df.pw.nausea[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.nausea$female_prop <- rowMeans(df.pw.nausea[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.nausea$anhedonia_baseline <- rowMeans(df.pw.nausea[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.nausea$anxiety_baseline <- rowMeans(df.pw.nausea[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.nausea$reward_baseline <- rowMeans(df.pw.nausea[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.nausea$colour <- ifelse(df.pw.nausea$treat1 %in% IMAO, 
                           'red', 
                           ifelse(df.pw.nausea$treat1 %in% RIMA,
                                  'orange',
                                  ifelse(df.pw.nausea$treat1 %in% DRI,
                                         'deepskyblue',
                                         ifelse(df.pw.nausea$treat1 %in% agonist,
                                                'purple',
                                                ifelse(df.pw.nausea$treat1 %in% vescicular,
                                                       'green4',
                                                       'grey'
                                                )))))
df.pw.nausea$group <- ifelse(df.pw.nausea$colour=='red',
                          'MAOI',
                          ifelse(df.pw.nausea$colour=='orange',
                                 'RIMA',
                                 ifelse(df.pw.nausea$colour=='deepskyblue',
                                        '*DRI',
                                        ifelse(df.pw.nausea$colour=='purple',
                                               'Agonist',
                                               ifelse(df.pw.nausea$colour=='green4',
                                                      'Vesicle transport facilitator',
                                                      'Other')))))
#run nausea meta-analysis
pwma.nausea <- metabin(n.e = n1, 
                    event.e = event1, 
                    n.c = n2, 
                    event.c = event2, 
                    studlab = studlab, 
                    data = df.pw.nausea, 
                    sm = 'OR', 
                    comb.fixed = F, 
                    comb.random = T, 
                    title = 'Nausea',
                    prediction = T, 
                    hakn = T, 
                    method.tau = 'REML',
                    subgroup = group)

```

```{r echo=FALSE, fig.width=12, fig.height=10}
forest(pwma.nausea, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'Nausea',
       col.square = pwma.nausea$data$colour
)
```
**Figure X** Forest plot for nausea for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.


### Secondary outcome: headache
```{r echo=FALSE, include=FALSE}
df.headache <- df[!is.na(df$headache), c('studlab', 
                                     'treatment', 
                                     'treatment_details', 
                                     'n_randomised', 
                                     'headache',
                                     'age_mean',
                                     'female_prop',
                                     'anhedonia_baseline_mean',
                                     'anxiety_baseline_mean',
                                     'reward_baseline_mean',
                                     'tx_duration',
                                     'arm')]
colnames(df.headache) <- c('studlab', 
                         'treatment', 
                         'treatment_details', 
                         'n', 
                         'r',
                         'age_mean',
                         'female_prop',
                         'anhedonia_baseline_mean',
                         'anxiety_baseline_mean',
                         'reward_baseline_mean',
                         'tx_duration',
                         'arm')
df.headache$treatment_details <- tolower(df.headache$treatment_details)
df.headache$treatment_details <- ifelse(df.headache$treatment_details=='placebo', 'placebo', 'active')
df.headache <- remove.onearm(df.headache)
df.headache.merged <- collapse.arms.binary(df.headache)
df.pw.headache <- netmeta::pairwise(studlab = studlab,
                                  treat = treatment,
                                  n = n,
                                  event = r,
                                  data = df.headache.merged,
                                  sm = 'OR')
df.pw.headache$age <- rowMeans(df.pw.headache[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.headache$female_prop <- rowMeans(df.pw.headache[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.headache$anhedonia_baseline <- rowMeans(df.pw.headache[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.headache$anxiety_baseline <- rowMeans(df.pw.headache[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.headache$reward_baseline <- rowMeans(df.pw.headache[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.headache$colour <- ifelse(df.pw.headache$treat1 %in% IMAO, 
                              'red', 
                              ifelse(df.pw.headache$treat1 %in% RIMA,
                                     'orange',
                                     ifelse(df.pw.headache$treat1 %in% DRI,
                                            'deepskyblue',
                                            ifelse(df.pw.headache$treat1 %in% agonist,
                                                   'purple',
                                                   ifelse(df.pw.headache$treat1 %in% vescicular,
                                                          'green4',
                                                          'grey'
                                                   )))))
df.pw.headache$group <- ifelse(df.pw.headache$colour=='red',
                             'MAOI',
                             ifelse(df.pw.headache$colour=='orange',
                                    'RIMA',
                                    ifelse(df.pw.headache$colour=='deepskyblue',
                                           '*DRI',
                                           ifelse(df.pw.headache$colour=='purple',
                                                  'Agonist',
                                                  ifelse(df.pw.headache$colour=='green4',
                                                         'Vesicle transport facilitator',
                                                         'Other')))))
#run headache meta-analysis
pwma.headache <- metabin(n.e = n1, 
                       event.e = event1, 
                       n.c = n2, 
                       event.c = event2, 
                       studlab = studlab, 
                       data = df.pw.headache, 
                       sm = 'OR', 
                       comb.fixed = F, 
                       comb.random = T, 
                       title = 'headache',
                       prediction = T, 
                       hakn = T, 
                       method.tau = 'REML',
                       subgroup = group)
```

```{r echo=FALSE, fig.width=12, fig.height=12}
forest(pwma.headache, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'headache',
       col.square = pwma.headache$data$colour
)
```
**Figure X** Forest plot for headache for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

### Secondary outcome: insomnia
```{r echo=FALSE, include=FALSE}
# insomnia ----
df.insomnia <- df[!is.na(df$insomnia), c('studlab', 
                                     'treatment', 
                                     'treatment_details', 
                                     'n_randomised', 
                                     'insomnia',
                                     'age_mean',
                                     'female_prop',
                                     'anhedonia_baseline_mean',
                                     'anxiety_baseline_mean',
                                     'reward_baseline_mean',
                                     'tx_duration',
                                     'arm')]
colnames(df.insomnia) <- c('studlab', 
                         'treatment', 
                         'treatment_details', 
                         'n', 
                         'r',
                         'age_mean',
                         'female_prop',
                         'anhedonia_baseline_mean',
                         'anxiety_baseline_mean',
                         'reward_baseline_mean',
                         'tx_duration',
                         'arm')
df.insomnia$treatment_details <- tolower(df.insomnia$treatment_details)
df.insomnia$treatment_details <- ifelse(df.insomnia$treatment_details=='placebo', 'placebo', 'active')
df.insomnia <- remove.onearm(df.insomnia)
df.insomnia.merged <- collapse.arms.binary(df.insomnia)
df.pw.insomnia <- netmeta::pairwise(studlab = studlab,
                                  treat = treatment,
                                  n = n,
                                  event = r,
                                  data = df.insomnia.merged,
                                  sm = 'OR')
df.pw.insomnia$age <- rowMeans(df.pw.insomnia[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.insomnia$female_prop <- rowMeans(df.pw.insomnia[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.insomnia$anhedonia_baseline <- rowMeans(df.pw.insomnia[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.insomnia$anxiety_baseline <- rowMeans(df.pw.insomnia[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.insomnia$reward_baseline <- rowMeans(df.pw.insomnia[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.insomnia$colour <- ifelse(df.pw.insomnia$treat1 %in% IMAO, 
                              'red', 
                              ifelse(df.pw.insomnia$treat1 %in% RIMA,
                                     'orange',
                                     ifelse(df.pw.insomnia$treat1 %in% DRI,
                                            'deepskyblue',
                                            ifelse(df.pw.insomnia$treat1 %in% agonist,
                                                   'purple',
                                                   ifelse(df.pw.insomnia$treat1 %in% vescicular,
                                                          'green4',
                                                          'grey'
                                                   )))))
df.pw.insomnia$group <- ifelse(df.pw.insomnia$colour=='red',
                             'MAOI',
                             ifelse(df.pw.insomnia$colour=='orange',
                                    'RIMA',
                                    ifelse(df.pw.insomnia$colour=='deepskyblue',
                                           '*DRI',
                                           ifelse(df.pw.insomnia$colour=='purple',
                                                  'Agonist',
                                                  ifelse(df.pw.insomnia$colour=='green4',
                                                         'Vesicle transport facilitator',
                                                         'Other')))))
#run insomnia meta-analysis
pwma.insomnia <- metabin(n.e = n1, 
                       event.e = event1, 
                       n.c = n2, 
                       event.c = event2, 
                       studlab = studlab, 
                       data = df.pw.insomnia, 
                       sm = 'OR', 
                       comb.fixed = F, 
                       comb.random = T, 
                       title = 'insomnia',
                       prediction = T, 
                       hakn = T, 
                       method.tau = 'REML',
                       subgroup = group)
```

```{r echo=FALSE, fig.width=12, fig.height=10}
forest(pwma.insomnia, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'insomnia',
       col.square = pwma.insomnia$data$colour
)
```
**Figure X** Forest plot for insomnia for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

### Secondary outcome:dry mouth
```{r echo=FALSE, include=FALSE}
# dry_mouth ----
df.dry_mouth <- df[!is.na(df$dry_mouth), c('studlab', 
                                     'treatment', 
                                     'treatment_details', 
                                     'n_randomised', 
                                     'dry_mouth',
                                     'age_mean',
                                     'female_prop',
                                     'anhedonia_baseline_mean',
                                     'anxiety_baseline_mean',
                                     'reward_baseline_mean',
                                     'tx_duration',
                                     'arm')]
colnames(df.dry_mouth) <- c('studlab', 
                         'treatment', 
                         'treatment_details', 
                         'n', 
                         'r',
                         'age_mean',
                         'female_prop',
                         'anhedonia_baseline_mean',
                         'anxiety_baseline_mean',
                         'reward_baseline_mean',
                         'tx_duration',
                         'arm')
df.dry_mouth$treatment_details <- tolower(df.dry_mouth$treatment_details)
df.dry_mouth$treatment_details <- ifelse(df.dry_mouth$treatment_details=='placebo', 'placebo', 'active')
df.dry_mouth <- remove.onearm(df.dry_mouth)
df.dry_mouth.merged <- collapse.arms.binary(df.dry_mouth)
df.pw.dry_mouth <- netmeta::pairwise(studlab = studlab,
                                  treat = treatment,
                                  n = n,
                                  event = r,
                                  data = df.dry_mouth.merged,
                                  sm = 'OR')
df.pw.dry_mouth$age <- rowMeans(df.pw.dry_mouth[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.dry_mouth$female_prop <- rowMeans(df.pw.dry_mouth[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.dry_mouth$anhedonia_baseline <- rowMeans(df.pw.dry_mouth[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.dry_mouth$anxiety_baseline <- rowMeans(df.pw.dry_mouth[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.dry_mouth$reward_baseline <- rowMeans(df.pw.dry_mouth[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.dry_mouth$colour <- ifelse(df.pw.dry_mouth$treat1 %in% IMAO, 
                              'red', 
                              ifelse(df.pw.dry_mouth$treat1 %in% RIMA,
                                     'orange',
                                     ifelse(df.pw.dry_mouth$treat1 %in% DRI,
                                            'deepskyblue',
                                            ifelse(df.pw.dry_mouth$treat1 %in% agonist,
                                                   'purple',
                                                   ifelse(df.pw.dry_mouth$treat1 %in% vescicular,
                                                          'green4',
                                                          'grey'
                                                   )))))
df.pw.dry_mouth$group <- ifelse(df.pw.dry_mouth$colour=='red',
                             'MAOI',
                             ifelse(df.pw.dry_mouth$colour=='orange',
                                    'RIMA',
                                    ifelse(df.pw.dry_mouth$colour=='deepskyblue',
                                           '*DRI',
                                           ifelse(df.pw.dry_mouth$colour=='purple',
                                                  'Agonist',
                                                  ifelse(df.pw.dry_mouth$colour=='green4',
                                                         'Vesicle transport facilitator',
                                                         'Other')))))
#run dry mouth meta-analysis
pwma.dry_mouth <- metabin(n.e = n1, 
                       event.e = event1, 
                       n.c = n2, 
                       event.c = event2, 
                       studlab = studlab, 
                       data = df.pw.dry_mouth, 
                       sm = 'OR', 
                       comb.fixed = F, 
                       comb.random = T, 
                       title = 'dry_mouth',
                       prediction = T, 
                       hakn = T, 
                       method.tau = 'REML',
                       subgroup = group)
```
```{r echo=FALSE, fig.width=12, fig.height=10}
forest(pwma.dry_mouth, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'dry_mouth',
       col.square = pwma.dry_mouth$data$colour
)
```
**Figure X** Forest plot for dry mouth for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

### Secondary outcome:constipation
```{r echo=FALSE, include=FALSE}
# constipation ----
df.constipation <- df[!is.na(df$constipation), c('studlab', 
                                     'treatment', 
                                     'treatment_details', 
                                     'n_randomised', 
                                     'constipation',
                                     'age_mean',
                                     'female_prop',
                                     'anhedonia_baseline_mean',
                                     'anxiety_baseline_mean',
                                     'reward_baseline_mean',
                                     'tx_duration',
                                     'arm')]
colnames(df.constipation) <- c('studlab', 
                         'treatment', 
                         'treatment_details', 
                         'n', 
                         'r',
                         'age_mean',
                         'female_prop',
                         'anhedonia_baseline_mean',
                         'anxiety_baseline_mean',
                         'reward_baseline_mean',
                         'tx_duration',
                         'arm')
df.constipation$treatment_details <- tolower(df.constipation$treatment_details)
df.constipation$treatment_details <- ifelse(df.constipation$treatment_details=='placebo', 'placebo', 'active')
df.constipation <- remove.onearm(df.constipation)
df.constipation.merged <- collapse.arms.binary(df.constipation)
df.pw.constipation <- netmeta::pairwise(studlab = studlab,
                                  treat = treatment,
                                  n = n,
                                  event = r,
                                  data = df.constipation.merged,
                                  sm = 'OR')
df.pw.constipation$age <- rowMeans(df.pw.constipation[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.constipation$female_prop <- rowMeans(df.pw.constipation[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.constipation$anhedonia_baseline <- rowMeans(df.pw.constipation[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.constipation$anxiety_baseline <- rowMeans(df.pw.constipation[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.constipation$reward_baseline <- rowMeans(df.pw.constipation[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.constipation$colour <- ifelse(df.pw.constipation$treat1 %in% IMAO, 
                              'red', 
                              ifelse(df.pw.constipation$treat1 %in% RIMA,
                                     'orange',
                                     ifelse(df.pw.constipation$treat1 %in% DRI,
                                            'deepskyblue',
                                            ifelse(df.pw.constipation$treat1 %in% agonist,
                                                   'purple',
                                                   ifelse(df.pw.constipation$treat1 %in% vescicular,
                                                          'green4',
                                                          'grey'
                                                   )))))
df.pw.constipation$group <- ifelse(df.pw.constipation$colour=='red',
                             'MAOI',
                             ifelse(df.pw.constipation$colour=='orange',
                                    'RIMA',
                                    ifelse(df.pw.constipation$colour=='deepskyblue',
                                           '*DRI',
                                           ifelse(df.pw.constipation$colour=='purple',
                                                  'Agonist',
                                                  ifelse(df.pw.constipation$colour=='green4',
                                                         'Vesicle transport facilitator',
                                                         'Other')))))
#run constipation meta-analysis
pwma.constipation <- metabin(n.e = n1, 
                       event.e = event1, 
                       n.c = n2, 
                       event.c = event2, 
                       studlab = studlab, 
                       data = df.pw.constipation, 
                       sm = 'OR', 
                       comb.fixed = F, 
                       comb.random = T, 
                       title = 'constipation',
                       prediction = T, 
                       hakn = T, 
                       method.tau = 'REML',
                       subgroup = group)
```
```{r echo=FALSE, fig.width=12, fig.height=9}
forest(pwma.constipation, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'constipation',
       col.square = pwma.constipation$data$colour
)
```
**Figure X** Forest plot for constipation for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

### Secondary outcome: dizziness
```{r echo=FALSE, include=FALSE}
df.dizziness <- df[!is.na(df$dizziness), c('studlab', 
                                     'treatment', 
                                     'treatment_details', 
                                     'n_randomised', 
                                     'dizziness',
                                     'age_mean',
                                     'female_prop',
                                     'anhedonia_baseline_mean',
                                     'anxiety_baseline_mean',
                                     'reward_baseline_mean',
                                     'tx_duration',
                                     'arm')]
colnames(df.dizziness) <- c('studlab', 
                         'treatment', 
                         'treatment_details', 
                         'n', 
                         'r',
                         'age_mean',
                         'female_prop',
                         'anhedonia_baseline_mean',
                         'anxiety_baseline_mean',
                         'reward_baseline_mean',
                         'tx_duration',
                         'arm')
df.dizziness$treatment_details <- tolower(df.dizziness$treatment_details)
df.dizziness$treatment_details <- ifelse(df.dizziness$treatment_details=='placebo', 'placebo', 'active')
df.dizziness <- remove.onearm(df.dizziness)
df.dizziness.merged <- collapse.arms.binary(df.dizziness)
df.pw.dizziness <- netmeta::pairwise(studlab = studlab,
                                  treat = treatment,
                                  n = n,
                                  event = r,
                                  data = df.dizziness.merged,
                                  sm = 'OR')
df.pw.dizziness$age <- rowMeans(df.pw.dizziness[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.dizziness$female_prop <- rowMeans(df.pw.dizziness[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.dizziness$anhedonia_baseline <- rowMeans(df.pw.dizziness[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.dizziness$anxiety_baseline <- rowMeans(df.pw.dizziness[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.dizziness$reward_baseline <- rowMeans(df.pw.dizziness[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.dizziness$colour <- ifelse(df.pw.dizziness$treat1 %in% IMAO, 
                              'red', 
                              ifelse(df.pw.dizziness$treat1 %in% RIMA,
                                     'orange',
                                     ifelse(df.pw.dizziness$treat1 %in% DRI,
                                            'deepskyblue',
                                            ifelse(df.pw.dizziness$treat1 %in% agonist,
                                                   'purple',
                                                   ifelse(df.pw.dizziness$treat1 %in% vescicular,
                                                          'green4',
                                                          'grey'
                                                   )))))
df.pw.dizziness$group <- ifelse(df.pw.dizziness$colour=='red',
                             'MAOI',
                             ifelse(df.pw.dizziness$colour=='orange',
                                    'RIMA',
                                    ifelse(df.pw.dizziness$colour=='deepskyblue',
                                           '*DRI',
                                           ifelse(df.pw.dizziness$colour=='purple',
                                                  'Agonist',
                                                  ifelse(df.pw.dizziness$colour=='green4',
                                                         'Vesicle transport facilitator',
                                                         'Other')))))
#run dizziness meta-analysis
pwma.dizziness <- metabin(n.e = n1, 
                       event.e = event1, 
                       n.c = n2, 
                       event.c = event2, 
                       studlab = studlab, 
                       data = df.pw.dizziness, 
                       sm = 'OR', 
                       comb.fixed = F, 
                       comb.random = T, 
                       title = 'dizziness',
                       prediction = T, 
                       hakn = T, 
                       method.tau = 'REML',
                       subgroup = group)
```

```{r echo=FALSE, fig.width=12, fig.height=10}
forest(pwma.dizziness, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'dizziness',
       col.square = pwma.dizziness$data$colour
)
```
**Figure X** Forest plot for dizziness for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

### Secondary outcome: vomiting
```{r echo=FALSE, include=FALSE}
df.vomiting <- df[!is.na(df$vomiting), c('studlab', 
                                     'treatment', 
                                     'treatment_details', 
                                     'n_randomised', 
                                     'vomiting',
                                     'age_mean',
                                     'female_prop',
                                     'anhedonia_baseline_mean',
                                     'anxiety_baseline_mean',
                                     'reward_baseline_mean',
                                     'tx_duration',
                                     'arm')]
colnames(df.vomiting) <- c('studlab', 
                         'treatment', 
                         'treatment_details', 
                         'n', 
                         'r',
                         'age_mean',
                         'female_prop',
                         'anhedonia_baseline_mean',
                         'anxiety_baseline_mean',
                         'reward_baseline_mean',
                         'tx_duration',
                         'arm')
df.vomiting$treatment_details <- tolower(df.vomiting$treatment_details)
df.vomiting$treatment_details <- ifelse(df.vomiting$treatment_details=='placebo', 'placebo', 'active')
df.vomiting <- remove.onearm(df.vomiting)
df.vomiting.merged <- collapse.arms.binary(df.vomiting)
df.pw.vomiting <- netmeta::pairwise(studlab = studlab,
                                  treat = treatment,
                                  n = n,
                                  event = r,
                                  data = df.vomiting.merged,
                                  sm = 'OR')
df.pw.vomiting$age <- rowMeans(df.pw.vomiting[, c('age_mean1', 'age_mean2')], na.rm = T)
df.pw.vomiting$female_prop <- rowMeans(df.pw.vomiting[, c('female_prop1', 'female_prop2')], na.rm = T)
df.pw.vomiting$anhedonia_baseline <- rowMeans(df.pw.vomiting[, c('anhedonia_baseline_mean1', 'anhedonia_baseline_mean2')], na.rm = T)
df.pw.vomiting$anxiety_baseline <- rowMeans(df.pw.vomiting[, c('anxiety_baseline_mean1', 'anxiety_baseline_mean2')], na.rm = T)
df.pw.vomiting$reward_baseline <- rowMeans(df.pw.vomiting[, c('reward_baseline_mean1', 'reward_baseline_mean2')], na.rm = T)
df.pw.vomiting$colour <- ifelse(df.pw.vomiting$treat1 %in% IMAO, 
                              'red', 
                              ifelse(df.pw.vomiting$treat1 %in% RIMA,
                                     'orange',
                                     ifelse(df.pw.vomiting$treat1 %in% DRI,
                                            'deepskyblue',
                                            ifelse(df.pw.vomiting$treat1 %in% agonist,
                                                   'purple',
                                                   ifelse(df.pw.vomiting$treat1 %in% vescicular,
                                                          'green4',
                                                          'grey'
                                                   )))))
df.pw.vomiting$group <- ifelse(df.pw.vomiting$colour=='red',
                             'MAOI',
                             ifelse(df.pw.vomiting$colour=='orange',
                                    'RIMA',
                                    ifelse(df.pw.vomiting$colour=='deepskyblue',
                                           '*DRI',
                                           ifelse(df.pw.vomiting$colour=='purple',
                                                  'Agonist',
                                                  ifelse(df.pw.vomiting$colour=='green4',
                                                         'Vesicle transport facilitator',
                                                         'Other')))))
#run vomiting meta-analysis
pwma.vomiting <- metabin(n.e = n1, 
                       event.e = event1, 
                       n.c = n2, 
                       event.c = event2, 
                       studlab = studlab, 
                       data = df.pw.vomiting, 
                       sm = 'OR', 
                       comb.fixed = F, 
                       comb.random = T, 
                       title = 'vomiting',
                       prediction = T, 
                       hakn = T, 
                       method.tau = 'REML',
                       subgroup = group)
```

```{r echo=FALSE, fig.width=12, fig.height=5}
forest(pwma.vomiting, 
       sortvar = seTE, 
       print.I2.ci = T, 
       label.e = 'Intervention', 
       label.c = 'Placebo', 
       label.left = 'Favours intervention',
       label.right = "Favours placebo",
       smlab = 'vomiting',
       col.square = pwma.vomiting$data$colour
)
```
**Figure X** Forest plot for vomiting for the comparison of dopaminergic agonists vs placebo at 4-12 weeks. OR: odds ratio, 95%CI: 95% confidence intervals.

## Subgroup analyses and meta-regressions

## Reporting bias

## Summary of evidence tables

## Abbreviations

## References